\sysfull

### 2018-08-02 paper/asplos19/background.tex
restructure the paper directory

\begin{wrapfigure}{t!}{0.5\textwidth}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example}
		\caption{Simplified C code snippet of a CRC calculation from~\cite{hicks_mibench2_2016}: per-byte message division by a polynomial; \texttt{NV} denotes non-volatile variable declaration.}\label{fig:crc_example}
	\end{subfigure}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example_war}
		\caption{Execution steps of the loop body in the snippet above: non-volatile checkpointing did not guarantee data consistency as data has been manipulated (line 9) with stale reminder (line 3)}\label{fig:crc_example_war}
	\end{subfigure}
	\caption{Code example demonstrating checkpointing gives rise to data inconsistency.}\label{fig:code_demo_incosistency}
\end{wrapfigure}
%\end{figure}

@@

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Model & Data Copied to/from NVRAM \\
		\hline\hline
		Mementos~\cite{mementos}	& Registers + Stack     \\
		DINO~\cite{dino}	& Registers + Stack + WAR NV variables used in task\\
		Chain~\cite{chain}	& PC + NV variables used in task\\
		Alpaca~\cite{alpaca}	& PC + WAR NV variables used in task\\
		Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
		Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
		\hline
	\end{tabular}
	\caption{Non-volatile memory access for data consistency; \emph{PC}: program counter, \emph{WAR variables}: variables involved in Write after Read (WAR) dependences, \emph{NV}: non-volatile.}
	\label{table:chechpoint_comparison}
\end{table}

\textbf{Frequent Non-volatile Memory Access.} 
Previous systems frequently access the non-volatile memory directly, which 
is a potential source of inefficiency.  Checkpointing systems copy all volatile
state~\cite{dino, mementos, ratchet, hicks_isca_2017} to non-volatile memory at
every checkpoint.  Task-based models, which do not take checkpoints, back up a
subset of non-volatile data to maintain memory consistency using, e.g.,
redo-logging.  Table~\ref{table:chechpoint_comparison} summarizes the data that
gets copies to and from the non-volatile memory in service of memory
consistency and progress preservation.  Ratchet~\cite{ratchet} and
Clank~\cite{hicks_isca_2017}, which require all memory to be non-volatile
perform high frequency non-volatile memory accesses, in to checkpointing
frequently.

@@

\textbf{Incorrectly Sized Tasks.} Compiler-inserted checkpoints or
programmer-defined tasks can both both incorrect and non-terminating or
inefficient.  If code between consecutive checkpoints or in a task (we refer to
both scenarios as ''code in a task'' in this section) consumes {\em more}
energy than the fixed, maximum energy that the device can buffer, then the task
will never be able to complete using buffered energy.  Such a task is
non-terminating, {\em prevents forward progress}, and makes the program
incorrect. 
%
If the task consumes far {\em less} energy than a device can buffer, the system
may operate {\em inefficiently}, checkpointing or transitioning between tasks
more often than needed. 
%
Avoiding excessively costly, non-terminating tasks and short, high-overhead
tasks is challenging both to the programmer and the compiler, because
estimating the exact energy use of an arbitrary code is complicated.  When {\em
porting} a program from one platform to another, the problem becomes worse
because an excessively costly task on one device may be a relatively short task
on a device with a larger buffer.  Buffer sizes on different platforms vary
widely from, e.g., 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo},
complicating the problem.
%
As a solution, \sys's execution model presents {\em task coalescing}, which
merges multiple tasks to amortize the overhead when tasks are too small, and
{\em task downscaling}, which breaks up a task when the task is too large to complete. 
%When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing} and {\em task downscaling}.  Coalescing dynamically merges multiple tasks based on execution behavior to amortize the cost of committing each task separately. Downscaling breaks up a single task into multiple subtasks that commit individually to avoid executing a single task that is too large to complete using the device's buffered energy.  Section~\ref{sec:task_adaptation}describes \sys's adaptive coalescing and downscaling mechanisms in detail. The main enabler for \sys's adaptation is its novel \emph{memory virtualization} mechanism, which is described in Section~\ref{sec:memory_virtulaization}.

>>>>

% \begin{wrapfigure}{t!}{0.5\textwidth}
\begin{figure}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example}
		\caption{Simplified C code snippet of a CRC calculation from~\cite{hicks_mibench2_2016}: per-byte message division by a polynomial; \texttt{NV} denotes non-volatile variable declaration.}\label{fig:crc_example}
	\end{subfigure}
	\begin{subfigure}[t]{\linewidth}
		\centering \includegraphics[width=\columnwidth]{figures/crc_example_war}
		\caption{Execution steps of the loop body in the snippet above: non-volatile checkpointing did not guarantee data consistency as data has been manipulated (line 9) with stale reminder (line 3)}\label{fig:crc_example_war}
	\end{subfigure}
	\caption{Code example demonstrating checkpointing gives rise to data inconsistency.}\label{fig:code_demo_incosistency}
% \end{wrapfigure}
\end{figure}

@@

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Model & Data Copied to/from NVRAM \\
		\hline\hline
		Mementos~\cite{mementos}	& Registers + Stack     \\
		DINO~\cite{dino}	& Registers + Stack + WAR NV variables \\%used in task\\
		Chain~\cite{chain}	& PC + NV variables used in task\\
		Alpaca~\cite{alpaca}	& PC + WAR NV variables used in task\\
		Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
		Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
		\hline
	\end{tabular}
	\caption{Non-volatile memory access for data consistency; \emph{PC}: program counter, \emph{WAR variables}: variables involved in Write after Read (WAR) dependences, \emph{NV}: non-volatile.}
	\label{table:chechpoint_comparison}
\end{table}

\textbf{Frequent Non-volatile Memory Access.} 
Previous systems frequently access the non-volatile memory directly, which 
is a potential source of inefficiency.  Checkpointing systems copy all volatile
state~\cite{dino, mementos, ratchet, hicks_isca_2017} to non-volatile memory at
every checkpoint.  Task-based models, which do not take checkpoints, back up a
subset of non-volatile data to maintain memory consistency using, e.g.,
redo-logging.  Table~\ref{table:chechpoint_comparison} summarizes the data that
gets copied to and from the non-volatile memory in service of memory
consistency and progress preservation.  Ratchet~\cite{ratchet} and
Clank~\cite{hicks_isca_2017}, which require all memory to be non-volatile
perform high frequency non-volatile memory accesses, into checkpointing
frequently.

@@

\textbf{Incorrectly Sized Tasks.} Compiler-inserted checkpoints or
programmer-defined tasks can both both incorrect and non-terminating or
inefficient.  If code between consecutive checkpoints or in a task (we refer to
both scenarios as ''code in a task'' in this section) consumes {\em more} than the fixed,
maximum energy that the device can buffer, then the task
will never be able to complete using buffered energy.  Such a task is
non-terminating, {\em prevents forward progress}, and makes the program
incorrect. 
%
If the task consumes far {\em less} energy than a device can buffer, the system
may operate {\em inefficiently}, checkpointing or transitioning between tasks
more often than needed. 
%
Avoiding excessively costly, non-terminating tasks and short, high-overhead
tasks is challenging both to the programmer and the compiler, because
estimating the exact energy use of an arbitrary code is complicated.  When {\em
porting} a program from one platform to another, the problem becomes worse
because an excessively costly task on one device may be a relatively short task
on a device with a larger buffer.  Buffer sizes on different platforms vary
widely from, e.g., 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo},
complicating the problem.
%
As a solution, \sys's execution model presents {\em task coalescing}, which
merges multiple tasks to amortize the overhead when tasks are too small, and
{\em task downscaling}, which breaks up a task when the task is too large to complete. 
%When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing} and {\em task downscaling}.  Coalescing dynamically merges multiple tasks based on execution behavior to amortize the cost of committing each task separately. Downscaling breaks up a single task into multiple subtasks that commit individually to avoid executing a single task that is too large to complete using the device's buffered energy.  Section~\ref{sec:task_adaptation}describes \sys's adaptive coalescing and downscaling mechanisms in detail. The main enabler for \sys's adaptation is its novel \emph{memory virtualization} mechanism, which is described in Section~\ref{sec:memory_virtulaization}.

### 2018-08-02 paper/asplos19/hwswsetup.tex
restructure the paper directory

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.65\columnwidth} |}
		\hline
		Application & No. tasks & SLOC & Description \\
		\hline\hline
        \textbf{ar} &10 &428 & Activity recognition using a nearest neighbor
classifier with a deterministic input from a randomly-generated sequence of
accelerometer data\\
		\hline
        \textbf{bc} &10 &371 & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} &14 &426 & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &5 &198 & Dijkstra shortest path algorithm executed on a
predefined adjacency matrix\\
		\hline
        \textbf{fft} &8 &449 & Fast Fourier Transform on three pre-generated 128
sample vectors\\
		\hline
		\textbf{sort} &4 &167 & Selection sort of a fixed sequence of numbers\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys.}
\label{table:benchmark_table}
\end{table}

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.54\columnwidth} |}
		\hline
		App.&tasks&SLOC&Description\\
		\hline\hline
        \textbf{ar} &10 &428 & Activity recognition using a nearest neighbor
classifier\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
		\hline
        \textbf{bc} &10 &371 & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} &14 &426 & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
		\hline
        \textbf{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
		\hline
		\textbf{sort} &4 &167 & Selection sort algorithm\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys.}
\label{table:benchmark_table}
\end{table}

### 2018-08-02 paper/asplos19/implementation.tex
restructure the paper directory

\begin{table}
\centering
\begin{tabular}{| r | p{0.7\columnwidth} |}
	\hline
	{Method} & {Arguments} \\
	\hline\hline
	\texttt{COALA\_INIT}($t$) & $t \in \mathbf{T}$: task to be scheduled on the first boot \\
	\hline
	\texttt{COALA\_RUN}() & --- \\
	\hline
	\texttt{COALA\_TASK}($t$, $w_t$) & $t \in \mathbf{T}$: new task name, $w_t$: weight of task $t$ \\
	\hline
	\texttt{COALA\_NEXT\_TASK}($t$) & $t \in \mathbf{T}$ : task to be run next \\
	\hline
	\texttt{COALA\_PV}($p$, $v$ [, $s$]) & $p$: variable type, $v \in \mathbf{V}$: new protected variable name, $s$: array size \\
	\hline
	$u$ := \texttt{RP}($v$) & $v \in \mathbf{V}$: protected variable to be read, $u$: destination operand \\
	\hline	
	\texttt{WP}($v$) := $u$ &  $v \in \mathbf{V}$: protected variable to be written, $u$: source operand \\
	\hline
	\texttt{COALA\_SM}($p$, $m$ [, $s$]) & $p$: \texttt{struct} member's type, $m$: \texttt{struct} member's name, $s$: array size \\
	\hline
\end{tabular}
\caption{API summary; $\mathbf{T}$: set of all tasks, $\mathbf{V}$: set of all protected variables, $[, s]$: optional argument.}
\label{table:coala_api}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{| r | p{0.67\columnwidth} |}
	\hline
	{Method} & {Arguments} \\
	\hline\hline
	\texttt{INIT}($t$) & $t \in \mathbf{T}$: scheduled task on first boot \\
	\hline
	\texttt{RUN}() & --- \\
	\hline
	\texttt{TASK}($t$, $w_t$) & $t \in \mathbf{T}$: task name, $w_t$: weight of task $t$ \\
	\hline
	\texttt{NEXT\_TASK}($t$) & $t \in \mathbf{T}$ : task to be run next \\
	\hline
	\texttt{PV}($p$, $v$ [, $s$]) & $p$: variable type, $v \in \mathbf{V}$: new protected variable name, $s$: array size \\
	\hline
	$u$ := \texttt{RP}($v$) & $v \in \mathbf{V}$: protected variable to be read, $u$: destination operand \\
	\hline	
	\texttt{WP}($v$) := $u$ &  $v \in \mathbf{V}$: protected variable to be written, $u$: source operand \\
	\hline
	\texttt{SM}($p$, $m$ [, $s$]) & $p$: \texttt{struct} member's type, $m$: \texttt{struct} member's name, $s$: array size \\
	\hline
\end{tabular}
\caption{API summary; $\mathbf{T}$: set of all tasks, $\mathbf{V}$: set of all protected variables, $[, s]$: optional argument.}
\label{table:coala_api}
\end{table}

### 2018-08-02 paper/asplos19/texFigCode/sram-buffer.tex
restructure the paper directory

	\node[right = 0.5cm of sram] (ref) {};
	\node[draw,very thick,minimum width=8em, minimum height=25em, right = of ref] (fram1) {};

@@

	\node[draw,below = -2.7cm of fram1,minimum width=6em, minimum height=5em] (pagesTmp) {};
	\node[punkt,draw=none, below = -2.5cm of fram1,fill=black!5] (y2-fram) {y};
	\node[punkt,draw=none, below = 0.1cm of y2-fram,fill=black!5] (z2-fram) {z};

@@

	(pagesTmp.east) edge [->, bend right,dotted,thick] node{(6) \texttt{commit}} (pagesOrg2.east);

>>>>

	\node[right = 0.5cm of sram] (ref) {};
	\node[draw,very thick,minimum width=8em, minimum height=21em, right = of ref] (fram1) {};

@@

	\node[draw,dotted,below = -2.5cm of fram1,minimum width=6em, minimum height=5em] (pagesTmp) {};
	\node[punkt,draw=none, below = -2.2cm of fram1,fill=black!5] (y2-fram) {y};
	\node[punkt,draw=none, below = 0.1cm of y2-fram,fill=black!5] (z2-fram) {z};

@@

	(pagesTmp.east) edge [->, bend right,dotted,thick] node[yshift=-0.2cm]{(6) \texttt{commit}} (pagesOrg2.east);
